---
output: github_document
---

# genderAPI

```{r echo = FALSE}
library(badger)
```

<!-- badges: start --->

<!-- [![CRAN\_Status\_Badge](https://www.r-pkg.org/badges/version/covidsymptom)](https://cran.r-project.org/package=covidsymptom) -->
<!-- ![CRAN\Download\_Badge](https://cranlogs.r-pkg.org/badges/grand-total/covidsymptom) -->
<!-- `r badge_devel("csss-resultat/covidsymptom", "blue")` -->
<!-- `r badge_lifecycle("experimental", "orange")` -->
<!-- `r badge_last_commit("csss-resultat/covidsymptom")` -->

<!-- badges: end -->

<!-- ```{r, include = FALSE} -->
<!-- knitr::opts_chunk$set( -->
<!--   collapse = TRUE, -->
<!--   comment = "#>", -->
<!--   fig.path = "man/figures/README-", -->
<!--   out.width = "100%" -->
<!-- ) -->
<!-- ``` -->


The `genderAPI` R package is a wrapper for Gender-API.com, the biggest platform on the internet to estimate gender by name, surname and country of origin. 


## Installation

Development version of the package can be installed from Github with:

``` r
install.packages("remotes")
remotes::install_github("hugofitipaldi/genderAPI")
```
## Usage

First, you will need an API Key, you can create your free account [here](https://gender-api.com/en/). A free account at Gender-API.com gives you 500 credits for free every month.

```{r warning=FALSE, message=FALSE, eval = FALSE}
library(genderAPI)
get_gender(name = "Camila", country_code = "BR", api_key = your_api_key)

```

```
##     name country gender accuracy
## 1 camila      BR female       98
```
